Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-04 manuscript.tex
Clarify 'how many acini per lung' we chose [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/b6c94bd9b09a75063c29a39afcb8831a1724e180.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/b6c94bd9b09a75063c29a39afcb8831a1724e180/checks
https://github.com/habi/acinar-analysis-manuscript/runs/401092183

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b888dd09a43ba4c9cab06a58ba4001ff2b0c5b04}{habi/acinar-analysis-manuscript@b888dd0}
on December 4, 2020.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...b6c94bd9b09a75063c29a39afcb8831a1724e180}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b6c94bd9b09a75063c29a39afcb8831a1724e180/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b6c94bd9b09a75063c29a39afcb8831a1724e180}{habi/acinar-analysis-manuscript@b6c94bd}
on December 4, 2020.
